Social Participation Ontology: community documentation, enhancements and use examples

### 2015-01-12 paper.tex
arrumado detalhe da ultima tabela
atualizando com arrumacoes minimas na tabela final

@@

\ontologiaa  & \aan Ontology from the Brazilian name Ontologia do \aan \\ \hline

@@

      \pubby  & A Linked Data Frontend for dereferencing \uri s & -//- \\\hline

>>>>

  \vspace{-6mm}

@@

      \ontologiaa  & \aan\ Ontology. &  the name is a derivative from the Brazilian ``Ontologia do \aan''. It is small, simple and entirely linked to upper ontologies (classes and properties) \\ \hline

@@

      \pubby  & A Linked Data Front-end for dereferencing \uri s & -//- \\\hline
